---
title: "inovick_peercommentary_kenboru_01.html"
output: html_document
---
---
title: "inovick_peercommentary_kenboru_01.html"
output: html_document
author: Kenboru
---

## Challenge 1
```{r}
v1 <- "Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."
v2 <- gsub("[[:punct:]]", "", v1)
v3 <- strsplit(v2, " ")
v4 <- c(v3[[1]])
v5 <- v4[seq(from = 1, to = 22, by = 3)]
v5
```
## I am not sure if this method of extracting every third element is what is being asked of us, but it looks clean and I do not believe it is 'brute forcing' the problem.

## comment1- This worked way better than mine, I was having issues with syntax because I put each element in quotes, but I think what you did was better. Also it looked like assigning each action a vector as you go on is a good call. Sorry I don't have any critiques lol, I will actually try what you did for mine when I clean it up. Good job!
## Challenge 2
```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
x <- c(m[, 2], m[, 3], m[, 6])
x
x <- m[6:8, ]
x
x <- m[2, 2]:m[6, 9]
x
```
## comment2- this is pretty similar to what I did
## Challenge 3
```{r}
a <- array(data = 400:1, dim = c(5, 5, 4, 4))
a[1, 1, 1, 2]
a[2, 3, 2, ]
a[1:5, 1:5, 3, 3]
```

## Challenge 4
```{r}
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")

Strepsirhini <- list(Lorisoidea, Lemuroidea)
names(Strepsirhini) <- list("Lorisoidea", "Lemuroidea")
 
Tarsioidea <- c("Tarsiidae")

Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")

Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")

Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")

Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")
Primates
```
## comment3- when I did this taxonomy challenge, I got more syntax issues and I think I wasn't assigning vectors correctly? Sorry this has become a commentary on my own work instead of yours!! Yours looks really good and is workig super well and mine was just a struggle so I feel like I have nothing constructive to add to yours
## Challenge 5
```{r}
z <- c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2)
m2 <- matrix(data = z, nrow = 5, ncol = 3, byrow = TRUE)
df1 <- as.data.frame(m2)
df1
coerce1 <- as.logical(df1[, 2])
coerce2 <- as.factor(df1[, 3])
str(df1)
```
## To be honest, I am not sure what I should be expecting from the str() function here, so I am hoping that this is correct. I still don't quite grasp data frames...
## last comment- I think this is right
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




